### 2018-12-12 chapters/2-methods.tex
ref Figure -> Fig

The post-processing pipeline is outlined in figure~\ref{fig:pipeline}. An
example case with resulting standardized image and fitted parametric maps is
shown in figure~\ref{fig:pmap}. The in-house software used in fitting was
quality controlled for correctness with cross-comparison to independent
implementation and with visual inspections of parametric maps and distributions.

>>>>

The post-processing pipeline is outlined in Fig~\ref{fig:pipeline}. An
example case with resulting standardized image and fitted parametric maps is
shown in Fig~\ref{fig:pmap}. The in-house software used in fitting was
quality controlled for correctness with cross-comparison to independent
implementation and with visual inspections of parametric maps and distributions.

### 2018-12-12 chapters/3-results.tex
typo
ref Figure -> Fig

Some of the high-ranking features are visualized in Figure~\ref{fig:tmap}. In
addition, ROC curves for best statistical and texture features are presented in
Figure~\ref{fig:roc}.

@@

The final model proposed to differentiate low from high Gleason score PCa
includes the features from ADCₘ, K, and T₂w listed in S12. The expected
performance ROC is presented in Figure~\ref{fig:roc}.

>>>>

Some of the high-ranking features are visualized in Fig~\ref{fig:tmap}. In
addition, ROC curves for best statistical and texture features are presented in
Fig~\ref{fig:roc}.

@@

The final model proposed to differentiate low from high Gleason score PCa
includes the features from ADCₘ, K, and T₂w listed in Table~S12. The expected
performance ROC is presented in Fig~\ref{fig:roc}.
